Examining background gene lists in clusterProfiler - RNA-seq example

### 2024-05-31 analysis/analyse_rnaseq1.Rmd
minsetsize

  ora_up <- as.data.frame(enricher(gene = defup ,
    universe = bg,  maxGSSize = 500000, TERM2GENE = gs1,
    pAdjustMethod="fdr",  pvalueCutoff = 1, qvalueCutoff = 1  ))

@@

  ora_dn <- as.data.frame(enricher(gene = defdn ,
    universe = bg,  maxGSSize = 500000, TERM2GENE = gs1,
    pAdjustMethod="fdr",  pvalueCutoff = 1, qvalueCutoff = 1  ))

>>>>

  ora_up <- as.data.frame(enricher(gene = defup ,
    universe = bg, minGSSize = 5, maxGSSize = 500000, TERM2GENE = gs1,
    pAdjustMethod="fdr",  pvalueCutoff = 1, qvalueCutoff = 1  ))

@@

  ora_dn <- as.data.frame(enricher(gene = defdn ,
    universe = bg, minGSSize = 5, maxGSSize = 500000, TERM2GENE = gs1,
    pAdjustMethod="fdr",  pvalueCutoff = 1, qvalueCutoff = 1  ))
